\documentclass{bubbler}

\renewcommand{\bubblertitle}{%
\unbubskip
\underline{\bol{BRICK \& STEEL}}\br
\underline{\bol{FULL RETIRED}}
\rebubskip}
\renewcommand{\bubblercredit}{Written by}
\renewcommand{\bubblerauthor}{Stu Maschwitz}
\renewcommand{\bubblersource}{Story by KTM}
\renewcommand{\bubblerdraftdate}{1/27/2012}
\renewcommand{\bubblercontact}{%
\unbubskip
Next Level Productions\br
1588 Mission Dr.\br
Solvang, CA 93463
\rebubskip}

\begin{document}
\begin{script}

\contop

\seg{ACT I}

% Set up the characters and the story.

\scene[EXT][DAY]{BRICK'S PATIO}

A gorgeous day.  The sun is shining.  But BRICK BRADDOCK, retired police detective, is sitting quietly, contemplating -- something.

The SCREEN DOOR slides open and DICK STEEL, his former partner and fellow retiree, emerges with two cold beers.

\conv[][]{STEEL}{%
Beer's ready!}

\conv[O.S.][]{BRICK }{%
Are they cold?}

\conv[][]{STEEL}{%
Does a bear crap in the woods?}

Steel sits.  They laugh at the dumb joke.

\conv[][beer raised]{STEEL}{%
To retirement.}

\conv[][]{BRICK}{%
To retirement.}

They drink long and well from the beers.

And then there's a long beat.

\joinup{%
Longer than is funny.\br
Long enough to be depressing.}

The men look at each other.

\dia{%
\diaconv[][]{STEEL}{%
\lyric{Screw retirement.}}}{%
\diaconv[][]{BRICK}{%
\lyric{Screw retirement.}}}

\cut{SMASH CUT TO:}

\scene[INT][DAY]{TRAILER HOME}

This is the home of THE BOY BAND, AKA DAN and JACK.  They too are drinking beer, and counting the take from their last smash-and-grab.  Money, drugs, and ridiculous props are strewn about the table.

\begin{comment}
It was supposed to be Vietnamese, right?
\end{comment}

\conv[][in Vietnamese, subtitled]{JACK}{%
\ita{Did you know Brick and Steel are retired?}}

\conv[][]{DAN}{%
Then let's retire them.\br
\underline{Permanently}.}

Jack begins to argue vociferously in Vietnamese (?), But mercifully we...

\cut{CUT TO:}

\scene[EXT][DAY]{BRICK'S POOL}

\cut{Steel, in the middle of a heated phone call:}

\conv[][]{STEEL}{%
They're coming out of the woodwork!\br
\inconv{pause}\br
No, everybody we've put away!\br
\inconv{pause}\br
Point Blank Sniper?}

\scene[][]{SNIPER SCOPE PO}

From what seems like only INCHES AWAY.  \underline{Steel's face FILLS the \ita{Leupold Mark 4} scope}.

\conv[][]{STEEL}{%
The man's a myth!}

Steel turns and looks straight into the cross-hairs.

\conv[][oh crap]{STEEL}{%
Hello...}

\clearpage

\cut{CUT TO:}

\scene[][]{OPENING TITLE}

\encen{BRICK BRADDOCK}

\encen{\& DICK STEEL IN}

\encen{BRICK \& STEEL}

\encen{FULL RETIRED}

\cut{SMASH CUT TO:}

\scene[EXT][DAY]{WOODEN SHACK}

COGNITO, the criminal mastermind, is SLAMMED against the wall.

\conv[][]{COGNITO}{%
Woah woah woah, Brick and Steel!}

Sure enough, it's Brick and Steel, roughing up their favorite usual suspect.

\conv[][]{COGNITO}{%
What is it you want with me, DICK?}

Steel SMACKS him.

\conv[][]{STEEL}{%
Who's coming after us?}

\conv[][]{COGNITO}{%
Everyone's coming after you mate!  Scorpio, The Boy Band, Sparrow, Point Blank Sniper...}

As he rattles off the long list, Brick and Steel share a look.  This is going to be BAD.

\cut{CUT TO:}

\begin{comment}


\scene[INT][DAY]{GARAGE}

BRICK and STEEL get into Mom's PORSCHE, Steel at the wheel.  They pause for a beat, the gravity of the situation catching up with them.

\conv[][]{BRICK}{%
This is everybody we've ever put away.}

\conv[][starting the engine]{STEEL}{%
So much for retirement!}

They speed off.  To destiny!

\cut{CUT TO:}


\end{comment}

\scene[EXT][DAY]{PALATIAL MANSION}

An EXTREMELY HANDSOME MAN drinks a beer.

\quad Shirtless, unfortunately.

His minion approaches offscreen:

\conv[][]{McNION }{%
We found Brick and Steel!}

\conv[][]{HANDSOME MAN}{%
I want them dead.  DEAD!}

Beer flies.

\cut{BURN TO PINK.}

\encen{THE END}

\end{script}
\end{document}
